---
title: 'DATA-613: Dates And Times Homework'
author: "Max Calzada Munoz"
date: "1/16/2022"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(nycflights13)
library(lubridate)
library(dplyr)
library(ggplot2)
```

### 1)

```{r, message = FALSE}
("20210714" %--% "20220606")/days(1)
```

### 2)

```{r, message = FALSE}
("19880101" %--% "19881231")/days(1)
```

```{r, message = FALSE}
("19870101" %--% "19871231")/days(1)
```

### 3)

```{r, message = FALSE}
("19890101" %--% "19891231")/days(1)
```

### 4)

There is a months() function because every year has 12 months, so it is useful to be able to divide years by months. There is not a dmonths() function since not every month has the same number of days (and therefore not every month has the same number of weeks, hours, minutes, and seconds). The programmer would have to specify fpr which month they want to find the number of weeks/days/hours/minutes/seconds.

### 5)

```{r, message = FALSE}
(today() %--% "19620411")%/%years(1)
("19620411" %--% today())%/%years(1)

# How old is John?
h_age <- today() - ymd(19620411)
h_age
as.duration(h_age)
```

John is 59 years old

### 6)

```{r, message = FALSE}
#First, I need to make a function,
make_datetime_100 <- function(year, month, day, time) 
{
  make_datetime(year, month, day, time %/% 100, time %% 100)
}

#then i use the data once its a function.
flights %>% 
  filter(!is.na(dep_time), !is.na(arr_time)) %>% 
  mutate(
    arr_time = make_datetime_100(year, month, day, arr_time)
  ) %>% 
  select(origin, dest, carrier, arr_time) -> flights_dt

flights_dt %>%
  print(n=10)
```

### 7)

```{r, message = FALSE}
flights_dt %>%
  select(origin, dest, carrier, arr_time) %>%
  filter(origin == "LGA",
         dest == "DFW",
         carrier == "AA") %>%
  slice(115:125) %>%
  print()
```

### 8)

```{r, message = FALSE}
(ymd_hms("2013-01-09 19:17:00") - ymd_hms("2013-01-09 16:16:00"))
```
