---
title: 'DATA-613: Vectors, Lists, Functions Homework'
author: "Max Calzada Munoz, Grady Keene"
date: "1/28/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
```

## 1) - 4)

```{r, message = FALSE}
Vector1 <- (c( 10, 19, 121, 83, 63, 7, 77, 61, 51, 97, 123, 41))
Vector1
```

### 1)

For the vector given above, use and show **two methods** of R coding to extract the first 
element and the last element.

```{r, message = FALSE}
length(Vector1)

Vector1[c(1,12)]
```

Alternate Method

```{r, message = FALSE}
length(Vector1)

Vector1[c(1,length(Vector1))]
```

Alternate Method 2

```{r, message = FALSE}
Vector1[c(1, 12)]
Vector1[Vector1 == c(10, 41)]
```

### 2)

For the vector given above, use and show **two methods** of R coding to extract all of the 
elements that are less than 60.

```{r, message = FALSE}
Vector1[Vector1 < 60]
```

Alternate Method

```{r, message = FALSE}
Vector1[!(Vector1 >= 60)]
```

### 3)

For the vector given above, use and show **two methods** of R coding to extract all numbers 
that are not divisible by 2 or 3.

```{r, message = FALSE}
Vector1[!(Vector1 %% 2 == 0) & !(Vector1 %% 3 == 0)]
```

Alternate Method

```{r, message = FALSE}
Vector1[!(Vector1 == 10) & !(Vector1 == 51) & !(Vector1 == 63) & !(Vector1 == 123)]
```

### 4)

Use and show **two R coding methods** to confirm that Vector1 does not have missing values.

```{r, message = FALSE}
Vector1[is.na(Vector1)]
```

```{r, message = FALSE}
Vector1[!is.na(Vector1)]
```

## 5) - 7)

```{r}
myList <-  list(TRUE, 12.35, "pear", 48, c = 3:8, list(23, "team"))
myList
```

### 5) 

For the list given above, use and show R coding to confirm that “pear” is a character 
element.

```{r, message = FALSE}
typeof(myList[[3]])

str(myList[[3]]) 
```

### 6) 

For the list given above, use and show R coding to extract the first three elements of the list.

```{r, message = FALSE}
myList[1:3]
```

### 7)

Use the $ operator to extract the element “pear” from your list. Be sure to use and show 
required R code to produce the requested output.

```{r, message = FALSE}
# myList$"pear"
# myList$3

#Since the methods above don't work, I need to assign "pear" to a variable

myList <-  list(TRUE, 12.35, pear = "pear", 48, c = 3:8, list(23, "team"))
myList$pear
```

## 8) - 10)

### 8)

Use and show R code to write a function to solve the following quadratic equations by using 
the quadratic formula.  (all equations have two real number solutions)

#### 8a) x^2 - 3x - 28 = 0

```{r, message = FALSE}
a8 <- 1
b8 <- -3
c8 <- -28

fQuadPos <- function(a,b,c) {
(-b + sqrt(b^2-4*a*c))/(2*a)
}

fQuadNeg <- function(a,b,c) {
(-b - sqrt(b^2-4*a*c))/(2*a)
}

fQuadPos(a8,b8,c8)
fQuadNeg(a8,b8,c8)
```

#### 8b) x^2 + x - 30 = 0

```{r, message = FALSE}
a8 <- 1
b8 <- 1
c8 <- -30

fQuadPos(a8,b8,c8)
fQuadNeg(a8,b8,c8)
```

#### 8c) 3x^2 + 14x + 8 = 0

```{r, message = FALSE}
a8 <- 3
b8 <- 14
c8 <- 8

fQuadPos(a8,b8,c8)
fQuadNeg(a8,b8,c8)
```

#### 8d) 2x^2 + 11x + -6 = 0

(This is the same thing as 2x^2 + 11x = 6)

```{r, message = FALSE}
a8 <- 2
b8 <- 11
c8 <- -6

fQuadPos(a8,b8,c8)
fQuadNeg(a8,b8,c8)
```

### 8 Alternate Method

```{r, message = FALSE}

quad <- function(a, b, c){ 
pos <- ((-b) + sqrt((b^2) - 4*a*c)) / (2*a) 
neg <- ((-b) - sqrt((b^2) - 4*a*c)) / (2*a) 
print(pos) 
print(neg) 
} 
#a)  x2- 3x - 28 = 0                                                                                                                
quad(1, -3, -28)
#b)  x2 + x  - 30 = 0                                                                                                             
quad(1, 1, -30)

#c) 3x2+ 14x + 8 = 0
quad(3, 14, 8)

#d) 2x2+11x = 6
quad(2, 11, 0)

```


### 9)

```{r, message = FALSE}
tb <- tibble::tibble(x = 1:10, y = 10:1, z = y/2)
typeof(tb)
#> [1] "list"
attributes(tb)
```

```{r, message = FALSE}
tb
```

### 10) 

In statistics, the Interquartile Range is the difference between Q3 and Q1.  Now show and 
use map function coding to find the Interquartile Range for each column of the tibble from 
number 9.

```{r, message = FALSE}
tb_IQR <- vector("double", ncol(tb))   # 1. output
for (i in seq_along(tb)) {              # 2. sequence
  tb_IQR[[i]] <- IQR(tb[[i]])         # 3. body
}
tb_IQR
```
