---
title: "American University DATA-613 Functions Homework"
author: "Max Calzada Munoz, Grady Keene"
date: "1/22/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)


# library(tidyverse)
# library(nycflights13)
# library(dplyr)
```

### 1) 

Write a function that will find the sum of the natural log, the common log and a log of base 2 
for any given positive number. Use your function to find answers for the first five even integers.  
Show all details and structure of your function.  You should get five answers. The first two 
answers are 1.994177 and 3.988354. (Your output should show the other three)

```{r, message = FALSE}
#First, I'm going to make a vector
#that doubles the first five integers
#so we get the first five EVEN integers.

xi2 <- (1:5)*2

#Second, I'm going to code the function.
fx1 <- function(x) {
  log(x) + log10(x) + log2(x)
}


#Third, I'm going to use
#the vector in the function
#and use the function in the loop.

for (i in xi2) {
  print(fx1(i))
}
```

Method 2

```{r, message = FALSE}
#Altnerantively, I could mash all the steps into one step.
for (i in (1:5)*2) {
  print(log(i) + log10(i) + log2(i))
}
```

Method 3

```{r, message = FALSE}
sumeven <- function(x) {
  vector <- c()
  for (i in 1:length(x)) {
    if(x[i] %% 2 == 0) 
      return(log10(x) + log(x) +log2(x))
  }
}

sumeven(c(2, 4, 6, 8, 10))
```

### 2) 

Use the if-else structure to print the statement "This is a big number" if the square of a value 
is greater than or equal to 100 and the following statement is printed if the square of the 
number is less than 100, "This is not a big number”. Use and show values of assignment and if-
else structures that will output both statements.

```{r, message = FALSE}
checkBig <- function(x) {
  if (x^2 >= 100) {
    result <- "This is a big number"
  }
  else {
    result <- "This is not a big number"
  }
  return(result)
}

checkBig(5)
checkBig(14000605)
```

### 3)

For the following if-else-if coding structure, make an adjustment so that it prints "Team A 
won"

team_A <- 2 # Number of goals scored by Team A
team_B <- 2 # Number of goals scored by Team B

if (team_A > team_B){
  print ("Team A won")
} else if (team_A < team_B){
  print ("Team B won")
} else {
  "Team A & B tied"
}

```{r, message = FALSE}
team_A <- 3 # I made the 2 a 3
team_B <- 2 # Number of goals scored by Team B

if (team_A > team_B){
  print ("Team A won")
} else if (team_A < team_B){
  print ("Team B won")
} else {
  "Team A & B tied"
}
```

### 4) 

Write an if- else if- else sequence of commands that will output the following
statements and appropriate output; If a value is divisible by 3 and 5 the output
statement is "divisible by Three and Five", If a value is divisible by 3 and 4, 
the output statement is "divisible by Three and Four, If a value is a number that
does not fall into either category, the output statement should be  "neither".
Use your function to show output statements for values 16, 45, and 24.

```{r, message = FALSE}
divfunc <- function(x) {
  if (x %% 3 == 0 & x %% 5 == 0){
  print ("divisible by Three and Five")
} else if (x %% 3 == 0 & x %% 4 == 0){
  print ("divisible by Three and Four")
} else {
  "neither"
}
}

divfunc(16)
divfunc(45)
divfunc(24)

```

Alternate Method

```{r, message = FALSE}
check15and12 <- function(x) {
  if (x %% 15 == 0) {
    result <- "divisible by Three and Five"
  }
  else if (x %% 12 == 0) {
    result <- "divisible by Three and Four"
  }
  else {
    result <- "neither"
  }
  return(result)
}

check15and12(16)
check15and12(45)
check15and12(24)
```

### 5)

Use piping and a dplyr command show and use R code to produce the following modified 
`mpg` data table that contains only quantitative variables. 

Now use the “special loop coding chunk”, illustrated in class, to produce the variance for all 
variables of the modified data table.

```{r, message = FALSE}
mpgQuant <- mpg %>%
  select(displ, cyl, cty, hwy)

mpgQuant
```

```{r, message = FALSE}
mpgQvar <- vector("double", ncol(mpgQuant))
 for (i in seq_along(mpgQuant)) {
   mpgQvar[[i]] <- var(mpgQuant[[i]])
 }

 mpgQvar
```

Alternate Method

```{r, message = FALSE}
mpg %>%
  select_if(is.numeric) %>%
  select(!year) -> mpg2

mpg2
  
```

```{r, message = FALSE}
 var_func <- vector("double", ncol(mpg2))  
 for (i in seq_along(mpg2)) {            
   var_func[[i]] <- var(mpg2[[i]])      
 }
 var_func
```

### 6)

Construct a for loop (as illustrated in the notes) that will produce the difference between the 
cube and the square for each prime number between 10 and 30.  (There are 6 answers. The 
first answer is 1210, your for loop coding should produce the other five answers)

```{r, message = FALSE}
#First, produce produce prime numbers between 10 and 30

#The following function is from stack overflow
#https://stackoverflow.com/questions/3789968/generate-a-list-of-primes-up-to-a-certain-number

allPrime <- function(n) {
  primes <- rep(TRUE, n)
  primes[1] <- FALSE
  for (i in 1:sqrt(n)) {
    if (primes[i]) primes[seq(i^2, n, i)] <- FALSE
  }
  which(primes)
}

allPrime(30) -> p30
allPrime(10) -> p10

p10to30 <- setdiff(p30,p10) # observations in p30 that are not in p10
```

```{r, message = FALSE}
#Second, I'm going to build the function.

fx6 <- function(x) {
  x^3 - x^2
}
```

```{r, message = FALSE}
#Third, I'm going to use the function in the loop.

for (i in p10to30) {
  print(fx6(i))
}
```
